Software Ticket Quality

### 2017-10-31 proposal/mprop.tex
Add bib entries for two data quality assessment papers
Finish paper on data quality assessment

% \textbf{Thumbs Up or Thumbs Down}\cite{kitchenham1996software}:
% \begin{itemize}
%   \item \textbf{What were the goals?}
%   \item \textbf{What was the method?}
%   \item \textbf{What did they learn?}
%   \item \textbf{Relevance to our work}:
% \end{itemize}

@@

>>>>

@@

\textbf{Data Quality Assessment}\cite{pipino2002data}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the authors is to present ways of developing usable data
    quality metrics that organizations can implement in their own internal 
    processes.
  \item \textbf{What was the method?}
    They have researched previous methods of assessing data quality in information
    systems and they formulated general advice that can be directly implemented
    by organizations in their processes.
  \item \textbf{What did they learn?}
    They learned that there is no universal approach to assessing data quality
    as it heavily depends on the context where it is analysed.
  \item \textbf{Relevance to our work}: it shows how one can effectively measure
    data quality in information systems, thus we can apply it on the quality of
    the tickets we are analysing.
\end{itemize}

\textbf{Product perspective on total 
        Data Quality Assessment}\cite{wang1998product}:
\begin{itemize}
  \item \textbf{What were the goals?}

  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}
